Error Correction in a Phenomenological Fibonacci Anyon Quantum Code

### 2014-08-22 ising/Fibonacci/about.tex

\heading{Snake Diagrams}

@@

We fix $Q_n$ to be the points $\{(0, i/(n+1)) for i=1,...n\}$
then we define the line $L = \{(0, x) s.t. |x|\leq 1\}.$
Given a representative $f$ of an element of $MCG(D_n)$
we define the
snake diagram as the
image of $L$ under $f$.

It is a theorem (see \cite{Dehornoy02}) that such snake diagrams
correspond uniquely to elements of the mapping class group, and
hence to the braid group $B_n$.

@@

We measure charge in regions bounded by curves, ie. elements of
the first homology group $H_1(D_n).$

>>>>

\heading{Curve Diagrams}

@@

We fix $Q_n$ to be the points $\{(0, i/(n+1)) for i=1,...n\}$
then we define the line $L = \{(0, x) s.t. |x|\leq 1\}.$
Given a representative $f$ of an element of $MCG(D_n)$
we define the
curve diagram as the
image of $L$ under $f$.

It is a theorem (see \cite{Dehornoy02}) that such curve diagrams
correspond uniquely to elements of the mapping class group, and
hence to the braid group $B_n$.

@@

%We measure charge in regions bounded by curves, ie. elements of
%the first homology group $H_1(D_n).$
